\documentclass[letterpaper,12pt]{article}

% \usepackage[default]{comfortaa}
\usepackage{calligra}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}

\begin{document}

\begin{center}
  \textbf{Rohan Kapur} \\
  3525 Waxwing Way, Antioch, CA 94509 \\
  925-522-1818 \\
  rkapurschool@gmail.com \\
  April 27, 2024
\end{center}

\noindent
Dear Hiring Manager,\\
\indent I am quite elated to learn about recent software engineering job openings at Discord HQ. I've always been very interested in being able to work at Discord since the product is my primary platform of communication and I really enjoy using it on a daily basis. I also see my outgoing personality and uplifting energy fitting in well with the team based on what I've seen in public communications and the social media platforms. I would therefore love to contribute to Discord's development, particularly on the macOS and Linux platforms which I'm the most familiar with.\\
\indent I have extensive experience with programming web frameworks in Javascript and Python using the relevant libraries (Flask, Express.js, etc). I also have experience doing so while working with teams to create full-stack mobile applications while following proper Agile project management practices and proper repository management etiquette. I am also quite the stickler for extensive documentation as evident from the several projects I've contributed to, such as the choreographic programming research during the summer of 2023, so you can be sure that whatever I work on will be well-documented. I also really enjoy programming in general, having completed several competitive programming problems while engaging frequently in recreational programming to expand my knowledge. I also very much enjoy imparting my knowledge to others, which I have extensive formal experience doing through the several tutoring jobs I held while at UC Santa Cruz. And I'm a very quick learner as evident from my experience at F5 Networks, where I had to quickly get acquainted with several new development tools, such as Snowflake.\\
\indent I do hope all this demonstrates my potential to be an integral part of the Discord software engineering team, and thank you for your consideration! I look forward to hearing back soon! Feel free to reference my Github repositories as needed for viewing the significant contributions I've made to several projects. \\
Sincerely,\\
{\calligra Rohan Kapur}\\
Rohan Kapur

\end{document}